---
title: "Interaction"
author: "Shylo Burrell"
date: "09/01/2021"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(data.table)
library(ggplot2)
library(magrittr)
library(janitor)
library(here)
library(knitr)
library(kableExtra)

clean_names <- janitor::clean_names
here <- here::here

```

```{r}

#data_folder <- "interaction"
#data_from <- "interaction"
#file_name <- "interaction - testing.xlsx"

```


```{r}
#import data and create data table
 
file_path <- "/Users/sburrell/Documents/interaction/data/interaction - testing.xlsx"
interaction_data_raw <- read_excel(file_path,
                                     sheet = "data",
                                     range = "A1:Z476") %>%
  clean_names()  %>%
  data.table()
#View(interaction_data_table)
#relevant rows & columns
interaction_data <- interaction_data_raw[
  include == "yes", 
  !c(
    "include","doi", "quartile", "year", "issue", "jaw_tests", "jaw", "smb", "comment", "report",  "synergy_used", "antagonism_used",  "ixn_to_support_syn_ant"
    )]
```


```{r}
#add new column combining all tests performed
#remove NA's from post hoc column (not relevant)

interaction_data$all_tests <- ifelse(
  !is.na(interaction_data$post_hoc),
  paste(interaction_data$tests, interaction_data$post_hoc, sep = ","), 
  paste(interaction_data$tests) 
  )

#View(interaction_data)

```


```{r}
design_summary <- table(interaction_data$design, useNA = "ifany") %>%
  data.table() 
design_summary$percent <- design_summary$N/sum(design_summary$N)*100
kable(design_summary, col.names = c("design", "freq", "percent"), digits = c(1,1,1)) %>%
  kable_styling()
```


```{r}
data_availability_summary <- table(interaction_data$data_availability, useNA = "ifany") %>%
  data.table() 
data_availability_summary$percent <- data_availability_summary$N/sum(data_availability_summary$N)*100
kable(data_availability_summary, col.names = c("data_availability", "freq", "percent"), digits = c(1,1,1)) %>%
  kable_styling()
```


```{r}
analysis_summary <- table(interaction_data$analysis, useNA = "ifany") %>%
  data.table() 
analysis_summary$percent <- analysis_summary$N/sum(analysis_summary$N)*100
kable(analysis_summary, col.names = c("analysis", "freq", "percent"), digits = c(1,1,1)) %>%
  kable_styling()
```


```{r}
t_tests_summary <- table(interaction_data$t_tests, useNA = "ifany") %>%
  data.table() 
t_tests_summary$percent <- t_tests_summary$N/sum(t_tests_summary$N)*100
kable(t_tests_summary, col.names = c("t_tests", "freq", "percent"), digits = c(1,1,1)) %>%
  kable_styling()
```


```{r}
tests_summary <- table(interaction_data$tests, useNA = "ifany") %>%
  data.table() 
tests_summary$percent <- tests_summary$N/sum(tests_summary$N)*100
kable(tests_summary, col.names = c("tests", "freq", "percent"), digits = c(1,1,1)) %>%
  kable_styling()
```


```{r}
all_tests_summary <- table(interaction_data$all_tests, useNA = "ifany") %>%
  data.table() 
all_tests_summary$percent <- all_tests_summary$N/sum(all_tests_summary$N)*100
kable(all_tests_summary, col.names = c("all_tests", "freq", "percent"), digits = c(1,1,1)) %>%
  kable_styling()

```


```{r}
post_hoc_summary <- table(interaction_data$post_hoc) %>%
  data.table() 
post_hoc_summary$percent <- post_hoc_summary$N/sum(post_hoc_summary$N)*100
kable(post_hoc_summary, col.names = c("post_hoc", "freq", "percent"), digits = c(1,1,1)) %>%
  kable_styling()
```


```{r}
ixn_reported_summary <- table(interaction_data$ixn_reported, useNA = "ifany") %>%
  data.table() 
ixn_reported_summary$percent <- ixn_reported_summary$N/sum(ixn_reported_summary$N)*100
kable(ixn_reported_summary, col.names = c("ixn_reported", "freq", "percent"), digits = c(1, 1, 1)) %>%
  kable_styling()

```


### Comparisons

design by journal
```{r}

journal_vs_design <- ggplot(data = interaction_data,
                            aes(x =  design,
                                y = journal,
                                color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        axis.text.y = element_blank())

journal_vs_design

```

data availability by journal
```{r}

journal_vs_data_availability <- ggplot(data = interaction_data,
                                       aes(x =  data_availability,
                                           y = journal,
                                           color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
    theme(axis.text.y = element_blank())

journal_vs_data_availability

```


journal vs analysis
```{r}

journal_vs_analysis <- ggplot(data = interaction_data,
                                aes(x =  analysis,
                                    y = journal,
                                    color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
    theme(axis.text.y = element_blank())

journal_vs_analysis

```



t tests by journal
```{r}

journal_vs_t_tests <- ggplot(data = interaction_data,
                             aes(x =  t_tests,
                                 y = journal,
                                 color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.y = element_blank())

journal_vs_t_tests

```

tests by journal
```{r}
journal_vs_tests <- ggplot(data = interaction_data,
                           aes(x =  tests,
                               y = journal,
                               color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1)) #to view test names
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank())

journal_vs_tests

```

post hoc by journal
```{r}

journal_vs_post_hoc <- ggplot(data = interaction_data,
                              aes(x =  post_hoc,
                                  y = journal,
                                  color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        axis.text.y = element_blank())

journal_vs_post_hoc

```

all tests by journal
```{r}
journal_vs_all_tests <- ggplot(data = interaction_data,
                           aes(x =  all_tests,
                               y = journal,
                               color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  #theme(axis.text.x = element_text(angle = 90, hjust = 1)) #to view test names
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank())

journal_vs_all_tests

```

interaction by journal
```{r}

journal_vs_ixn_reported <- ggplot(data = interaction_data,
                                  aes(x =  ixn_reported,
                                      y = journal,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.y = element_blank())

journal_vs_ixn_reported


```

design by rank
```{r}
rank_vs_design <- ggplot(data = interaction_data,
                                  aes(x =  design,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

rank_vs_design
```


data availability by rank
```{r}
rank_vs_data_availability <- ggplot(data = interaction_data,
                                  aes(x = data_availability,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) 

rank_vs_data_availability
```

analysis by rank
```{r}
rank_vs_analysis <- ggplot(data = interaction_data,
                                  aes(x = analysis,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) 

rank_vs_analysis
```

t tests by rank
```{r}
rank_vs_t_tests <- ggplot(data = interaction_data,
                                  aes(x = t_tests,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) 

rank_vs_t_tests
```

tests by rank
```{r}
rank_vs_tests <- ggplot(data = interaction_data,
                                  aes(x = tests,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

rank_vs_tests
```

post hoc by rank
```{r}
rank_vs_post_hoc <- ggplot(data = interaction_data,
                                  aes(x = post_hoc,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

rank_vs_post_hoc
```

all tests by rank
```{r}
rank_vs_all_tests <- ggplot(data = interaction_data,
                                  aes(x = all_tests,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) +
  theme(axis.text.x = element_blank())
#axis.text.x = element_text(angle = 90, hjust = 1))

rank_vs_all_tests
```

interaction reported by rank
```{r}
rank_vs_ixn_reported<- ggplot(data = interaction_data,
                                  aes(x = ixn_reported,
                                      y = rank,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) 

rank_vs_ixn_reported
```

design vs data availability (color by journal)
```{r}

design_vs_data_availability_a <- ggplot(data = interaction_data,
                                      aes(x =  data_availability,
                                          y = design,
                                          color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) 

design_vs_data_availability_a 

```

design vs data availability (color by rank)
```{r}

design_vs_data_availability <- ggplot(data = interaction_data,
                                      aes(x =  data_availability,
                                          y = design,
                                          color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

design_vs_data_availability 

```

design vs analysis
```{r}

design_vs_analysis_a <- ggplot(data = interaction_data,
                               aes(x =  analysis,
                                   y = design,
                                   color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) 

design_vs_analysis_a
```

design vs analysis (color by tests)
```{r}
design_vs_analysis_b <- ggplot(data = interaction_data,
                               aes(x =  analysis,
                                   y = design,
                                   color = tests)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = FALSE) 

design_vs_analysis_b

```

design vs t tests
```{r}

design_vs_t_tests <- ggplot(data = interaction_data,
                            aes(x =  t_tests,
                                y = design,
                                color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

design_vs_t_tests


```


design vs tests
```{r}

design_vs_tests <- ggplot(data = interaction_data,
                            aes(x = tests,
                                y = design,
                                color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

design_vs_tests


```

design vs post hoc
```{r}
design_vs_post_hoc <- ggplot(data = interaction_data,
                             aes(x =  post_hoc,
                                 y = design,
                                 color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

design_vs_post_hoc
```
design vs all tests (color by rank)
```{r}

design_vs_all_tests <- ggplot(data = interaction_data,
                            aes(x = all_tests,
                                y = design,
                                color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.x = element_blank())
    #axis.text.x = element_text(angle = 90, hjust = 1))

design_vs_all_tests


```

design vs interaction reported

```{r}

design_vs_ixn_reported <- ggplot(data = interaction_data,
                                 aes(x =  ixn_reported,
                                     y = design,
                                     color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

design_vs_ixn_reported

```


data availability by analysis
```{r}

analysis_vs_data_availability <- ggplot(data = interaction_data,
                                        aes(x =  data_availability,
                                            y = analysis,
                                            color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

analysis_vs_data_availability 
```

data availability by t tests
```{r}

t_tests_vs_data_availability <- ggplot(data = interaction_data,
                                       aes(x =  data_availability,
                                           y = t_tests,
                                           color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

t_tests_vs_data_availability 

```

data availability by tests
```{r}

tests_vs_data_availability <- ggplot(data = interaction_data,
                                     aes(x =  data_availability,
                                         y = tests,
                                         color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

tests_vs_data_availability 

```

data availability by post hoc
```{r}

post_hoc_vs_data_availability <- ggplot(data = interaction_data,
                                        aes(x =  data_availability,
                                            y = post_hoc,
                                            color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

post_hoc_vs_data_availability 

```

data availability by all tests
```{r}

all_tests_vs_data_availability <- ggplot(data = interaction_data,
                                     aes(x =  data_availability,
                                         y = all_tests,
                                         color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

all_tests_vs_data_availability 

```

data availability vs interaction reported
```{r}
data_availability_vs_ixn_reported <- ggplot(data = interaction_data,
                                            aes(x =  ixn_reported,
                                                y = data_availability,
                                                color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

data_availability_vs_ixn_reported

```

analysis by t tests
```{r}

t_tests_vs_analysis <- ggplot(data = interaction_data,
                              aes(x =  analysis,
                                  y = t_tests,
                                  color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

t_tests_vs_analysis

```

analysis by tests
```{r}

tests_vs_analysis <- ggplot(data = interaction_data,
                            aes(x =  analysis,
                                y = tests,
                                color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

tests_vs_analysis


```

analysis by post hoc
```{r}

post_hoc_vs_analysis <- ggplot(data = interaction_data,
                               aes(x =  analysis,
                                   y = post_hoc,
                                   color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

post_hoc_vs_analysis

```

analysis by all tests
```{r}

all_tests_vs_analysis <- ggplot(data = interaction_data,
                            aes(x =  analysis,
                                y = all_tests,
                                color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

all_tests_vs_analysis


```


analysis vs interaction reported
```{r}

analysis_vs_ixn_reported <- ggplot(data = interaction_data,
                                   aes(x =  ixn_reported,
                                       y = analysis,
                                       color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

analysis_vs_ixn_reported

```

t tests vs tests
```{r}

tests_vs_t_tests <- ggplot(data = interaction_data,
                           aes(x =  t_tests,
                               y = tests,
                               color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

tests_vs_t_tests


```

t tests vs post hoc
```{r}

t_tests_vs_post_hoc <- ggplot(data = interaction_data,
                                  aes(x =  post_hoc,
                                      y = t_tests,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 
t_tests_vs_post_hoc

```


all tests vs t tests
```{r}

all_tests_vs_t_tests <- ggplot(data = interaction_data,
                           aes(x =  t_tests,
                               y = all_tests,
                               color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

all_tests_vs_t_tests


```

t tests vs interaction reported
```{r}

t_tests_vs_ixn_reported <- ggplot(data = interaction_data,
                                  aes(x =  ixn_reported,
                                      y = t_tests,
                                      color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

t_tests_vs_ixn_reported

```

tests vs post hoc
```{r}

tests_vs_post_hoc <- ggplot(data = interaction_data,
                                aes(x =  post_hoc,
                                    y = tests,
                                    color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

tests_vs_post_hoc

```

tests vs interaction reported
```{r}

tests_vs_ixn_reported <- ggplot(data = interaction_data,
                                aes(x =  ixn_reported,
                                    y = tests,
                                    color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

tests_vs_ixn_reported

```


```{r}

post_hoc_vs_ixn_reported <- ggplot(data = interaction_data,
                                   aes(x =  ixn_reported,
                                       y = post_hoc,
                                       color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

post_hoc_vs_ixn_reported
```


all tests vs interaction reported
```{r}

all_tests_vs_ixn_reported <- ggplot(data = interaction_data,
                                aes(x =  ixn_reported,
                                    y = all_tests,
                                    color = rank)) +
  geom_point(alpha = 0.5, show.legend = FALSE) +
  geom_jitter(width = 0.3, show.legend = TRUE) 

all_tests_vs_ixn_reported

```


```{r}
#png( "mygraph1.png", width = 864, height = 864)
#p <- ggplot(interaction_data, aes(ixn_reported, analysis)) + geom_point()

#p + facet_grid(vars(data_availability), vars(design))

```

```{r}
#png( "mygraph2.png", width = 2304, height = 1536)
#p <- ggplot(interaction_data, aes(ixn_reported, analysis)) + geom_point()

#p + facet_grid(vars(design), vars(rank))
```



Example 1: Estimation of a treatment effect relative to a control effect (“Something different”) 

Example 2: Estimation of the effect of background condition on an effect (“it depends”)

Example 3: Estimation of synergy (“More than the sum of the parts”)    
  used "synergy" and have data available:  
    https://doi.org/10.1126/scisignal.aay0482  
        data available is not what we need  
    https://doi.org/10.1038/s42255-019-0122-z  
      two-way anova for: fig 2d, i. 3k. 4h (longitudinal), 5d.  
    https://doi.org/10.1016/j.cell.2020.05.053  
      only factorial analysis was for longitudinal data  
    

